Illuminating a Dark Lens : A Type Ia Supernova Magnified by Galaxy Cluster Abell 2744

### 2015-01-22 snTomas.tex
added initial spec fit fig

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{FIG/discovery_image}
\caption{  
SN \tomas\ in the Abell 2744 field.  The left panel shows a
UV/Optical/IR color composite image constructed from all available HST
imaging of the Abell 2744 cluster field.\footnote{Image Credit: NASA,
ESA, and J. Lotz, M. Mountain, A. Koekemoer, and the HFF Team
(STScI)}  The inset panels at right show F814W imaging of the
immediate vicinity of SN \tomas, approximately 40\arcsec\ from the
center of the cluster.  The top panel shows the template image,
combining all data prior to the SN appearance.  Labeled ellipses mark the nearest galaxies and their redshift constraints: a photometric redshift for the most likely host galaxy is marked in blue, and the spectroscopic redshift for a likely background galaxy is given in yellow. The bottom panel is
constructed from all HFF F814W imaging taken while the SN was detectable, and marks the SN location with an arrow.}
\end{center}
\end{figure*}

SN \tomas\ was discovered in \HST\ observations with the Advanced
Camera for Surveys (ACS) in the F606W and F814W bands (V and i),
collected on UT 2014 May 15 as part of the Hubble Frontier Fields
(HFF) survey (PI:J.Lotz,
HST-PID:13495).\footnote{\url{http://www.stsci.edu/hst/campaigns/frontier-fields}}
The HFF program is a 3-year director's discretionary initiative that
is collecting 140 orbits of HST imaging (roughly 340 ksec) on six
massive galaxy clusters, plus 6 accompanying ``parallel fields.''
Each field is observed in 3 optical bands (ACS F435W, F606W and F814W)
and 4 infrared (IR) bands (WFC3-IR F105W, F125W, F140W, and F160W),
although the optical and IR imaging campaigns are separated by $\sim$6
months. Abell 2744 was the first cluster observed, with IR imaging
spanning 2013 October-November, and optical imaging from 2014
May-July.  A composite image of the HFF data showing the SN is
presented in Figure~\ref{fig:DiscoveryImage}.  The SN detection was
made in difference images, constructed using template imaging of Abell
2744 from HST+ACS observations taken in 2009 (PI:Dupke,
HST-PID:11689).

@@

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{FIG/discovery_image}
\caption{  \label{fig:DiscoveryImage}
SN \tomas\ in the Abell 2744 field.  The left panel shows a
UV/Optical/IR color composite image constructed from all available HST
imaging of the Abell 2744 cluster field.\footnote{Image Credit: NASA,
ESA, and J. Lotz, M. Mountain, A. Koekemoer, and the HFF Team
(STScI)}  The inset panels at right show F814W imaging of the
immediate vicinity of SN \tomas, approximately 40\arcsec\ from the
center of the cluster.  The top panel shows the template image,
combining all data prior to the SN appearance.  Labeled ellipses mark the nearest galaxies and their redshift constraints: a photometric redshift for the most likely host galaxy is marked in blue, and the spectroscopic redshift for a likely background galaxy is given in yellow. The bottom panel is
constructed from all HFF F814W imaging taken while the SN was detectable, and marks the SN location with an arrow.}
\end{center}
\end{figure*}

SN \tomas\ was discovered in \HST\ observations with the Advanced
Camera for Surveys (ACS) in the F606W and F814W bands (V and i),
collected on UT 2014 May 15 as part of the Hubble Frontier Fields
(HFF) survey (PI:J.Lotz,
HST-PID:13495).\footnote{\url{http://www.stsci.edu/hst/campaigns/frontier-fields}}
The HFF program is a 3-year director's discretionary initiative that
is collecting 140 orbits of HST imaging (roughly 340 ksec) on six
massive galaxy clusters, plus 6 accompanying ``parallel fields.''
Each field is observed in 3 optical bands (ACS F435W, F606W and F814W)
and 4 infrared (IR) bands (WFC3-IR F105W, F125W, F140W, and F160W),
although the optical and IR imaging campaigns are separated by $\sim$6
months. Abell 2744 was the first cluster observed, with IR imaging
spanning 2013 October-November, and optical imaging from 2014
May-July.  A composite image of the HFF data showing the SN is
presented in Figure~\ref{fig:DiscoveryImage}.  The SN detection was
made in difference images constructed using template imaging of Abell
2744 from HST+ACS observations taken in 2009 (PI:Dupke,
HST-PID:11689).

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{FIG/specfit}
\caption{  \label{fig:SpecFit}
Best-fit Type Ia spectral template matches to the SN \tomas\ spectrum.
When the templates are not warped, an acceptable fit can be found with
a normal Type Ia at $z\sim1$ (top), or at $z=1.31$ (middle).  Introducing a smooth 3rd-order polynomial to warp the shape of the template pseudo-continuum makes the $z=1.31$ solution far superior.}
\end{center}
\end{figure}
